Eleven years of student replication projects provide evidence on the correlates of replicability in psychology

### 2023-05-04 paper/manuscript.Rmd
another pass at intro and disc

Cumulative science requires foundational empirical results that are robust enough to support theory construction and future experimental extension. Scientists often treat publication in a scientific journal as a signal that a result was (likely to be) true, which leads scientists to build on findings without verifying them first.  The replication crisis called into question the tacit assumption that most of the literature was robust and would replicate. Certain prominent findings failed to replicate in multi-site replication attempts [ex. terror management theory, @klein2022; ego-depletion, @hagger2016], and a large-scale replication project pegged the replication rate for findings in top-tier psychology journals at around 40% [@openscienceconsortium2015].  When the trust in the literature mismatches the robustness results, many scientists can waste time and resources becoming frustrated pursuing extensions to a popular, but unreliable result. This seems to be the current situation of the literature, which leads to question: what do we do to minimize the waste?

From a policy perspective, we need to understand the landscape of the problem before we can have research-informed science policy interventions. Thus, we might want to know 1) what quantity to measure if we want to capture frustration and waste due to non-cumulative findings and 2) from a descriptive perspective, what types of studies are most at risk for this issue. Such measurements have been the focus of much prior work, but there is limited consensus on what is being estimated.

Three large-scale investigations have addressed replication rates in psychology. Reproducibility Project: Psychology, mentioned above, sampled roughly 100 studies from articles published in three top psychology journals in 2008 and they found an overall replication rate of around 40% [@openscienceconsortium2015]. ManyLabs investigated heterogeneity using short target studies that compared between two conditions each. These study designs were not representative of the psychology literature as a whole, and due to the heterogeneity goal, they had large overall samples across multiple sites. Across Many Labs 1-3, in these high-powered replications, only 29 of 51 target effects (57%) replicated [@klein2014; @klein2018; @ebersole2016]. @camerer2018 replicated all 21 behavioral social science studies from Nature and Science from 2010-2015 that were feasible; they consulted original authors and had high power to detect effects smaller than those reported. In this well-resourced environment with expert input, the replication rate was around 60%. These studies all measured replication rates, but the details of their methods and outcome measures varied.

@@

Rather than aim for some measure of "true" replicability, it makes more sense to contextualize replication efforts based on their methods and outcome measures. With this lens, we could say that RP:P is looking at how well findings in well-known journals can be replicated in typical circumstances. Many Labs looked at which well-known two conditions studies replicate with huge samples, and @camerer2018 was looking at what replicates when conducted in a highly-resourced environment with expert involvement. All of these are pontentially desirable estimands depending on what the specific circumstances and questions of interest are.

From the point of view of enabling cumulative science, an estimand of interest is how well work can be replicated by students, as students conduct most scientific work [@frank2022]. In our current study, we use student success at replicating an effect as our estimand. In particular, our estimand is the probability that a researcher, on selecting a finding of interest from the literature, can successfully achieve a result satisfactorily close enough to the original that they can build on it in their own work, with all the necessary compromises to the methods and sample of the original that may be required by the constraints of the situation.

Our replication approach reflects this estimand. Our sample of studies is selected based on what studies students were interested in and wanting to replicate, with some filtering for feasibility; this sampling reflects how scientists choose what studies to build on: those that are interesting and relatively doable given methodological and budgetary constraints.

We use a subjective replication score as our primary metric. Whether one feels confident in the results of a study given a replication is not always dependent on only one outcome measure (ex. interaction term) and particularly not dependent on only one statistical comparison between the two studies (ex. replication is p<.05 same direction as original). This metric avoids bright line distinctions and accommodates the range of outcome measures in our diverse set of studies.

All our replications were conducted under short time scales and relatively small budgets, paralleling the constraints many scientists are under when starting new projects. From the point of view of cumulative science, researchers want to know if they can get paradigms to work under their real-world constraints.

@@

Given the limitations of experimental approaches, we have to rely on correlational approaches for now.  Correlational approaches depend on data from replications, generally drawing heavily from the same small set of data points. In particular, the RP:P dataset itself is much discussed and reanalyzed [@etz2016;@gilbert2016;@patil2016;@anderson2016] to the point that much of what we think we know about replicability may be overfit to the 100 studies included in in RP:P. We need more data to find potential targets of concern and intervention.

Our contribution is a new dataset of 176 replications of experimental studies from the social sciences, primarily psychology. These replications were conducted by students in graduate-level experimental methods class between 2011 and 2022 as individual course projects. We investigated statistical and experimental-design predictors of replicability in this dataset and found that within-subjects designs and studies with large standardized effect sizes were positively correlated with replication success.

@@

## question, summary, and takehomes

NEED TO REDO! 
MAY NEED SMOOTHER TRANSITIONS THROUGHOUT
Prior large scale replications of psychology findings have estimated the replication rate at somewhere around one half, which intuitively feels low. However, limited numbers of replications and limited research into specific predictors of replication failure mean that the reasons for non-replications are not well understood.

Overall, we take a functional approach to assessing replicability, by framing both our methods and interpretation around the idea of whether work can be repeated or built on by an early-career scientist.

<!-- restatement of question -->

Here we took advantage of 11 years of graduate student replication projects to look at correlational predictors of replication in a previously-unused dataset. In line with previous results, we found a `r round(pluck(sub_rep_rate,1))`% replication rate, with some studies showing effect sizes similar to the original and others much smaller. When we looked at individual correlates of replicability, within-subjects designs, work in the subfield of cognitive psychology, and the original and replication both using online samples stood out as the strongest correlates. As many of these predictors interrelate with one another, we ran regularized regressions with all the predictors at once. Due to our small sample, model estimates were uncertain, but within-subjects designs and large original effect sizes were the strongest predictors.

<!-- contributions and takehome  -->
 The same issue that may cause a study not to replicate under constrained circumstances (despite hypothetically replicating under more favorable circumstances such as expert administration or larger budgets) will also plague attempts to build off those studies in constrained circumstances. Thus, we believe it is relevant to estimate replicability under the limitations of real world resource and expertise constraints. 
## intepretation - replication in light of the goal

Replication results should be interpreted in light of their methods and estimand.

Given our sample, we are able to estimate the correlates of studies replicating when the replications are conducted online, by graduate students with limited time and budget. We do not interpret our non-replications as indicating the original results were false positives (presumably some were and some weren't). There are many possible reasons for the non-replications in this sample. In some cases, the problem may be with the replication, such as too few participants, many exclusions for failed attention checks, or participants speeding through the study. When these issues are diagnosed, they suggest possible ways to "rescue" the replication by increasing the sample or changing the interface, without altering the underlying experiment; thus, while the replication did not succeed, after some troubleshooting, students may still be able to extend the work in the future. In other cases, there were a priori reasons to distrust the original study, such as exclusion criteria that seemed post-hoc or high-order interaction terms with a small sample. That said, not all scientists recognize the same factors as potential indications of low power or questionable research practices; students conducting these replications generally expected them to succeed. In many non-replication cases, it was unclear why the results failed to replicate.

## limitations

@@

## conclusion

>>>>

 Cumulative scientific progress requires empirical results that are robust enough to support theory construction and future extensions. Yet in psychology, some prominent individual findings have failed to replicate in multi-site replication attempts [ex. terror management theory, @klein2022; ego-depletion, @hagger2016], and a large-scale replication project pegged the replication rate for findings in top-tier psychology journals at around 40% [@openscienceconsortium2015]. When scientists treat publication as a signal of truth and attempt to build on results without verifying them first, they can become frustrated pursuing extensions to a popular, but unreliable result. As each failed extension does not directly contradict the original result, many scientists may waste a lot of time and resources pursuing results where there may be none. This leads to a question: what do we do to minimize the waste?

[This feels like we're setting up for the advice: don't try to extend anything without replicating it first, not sure how to shift to the policy issue.]

From a policy perspective, we need to understand the landscape of the problem before we can have research-informed science policy interventions. Thus, we might want to know 1) what quantity to measure if we want to capture frustration and waste due to non-cumulative findings and 2) from a descriptive perspective, what types of studies are most at risk for this issue. Such measurements have been the focus of much prior work around replicability, but there is limited consensus on what is being estimated.

Three large-scale investigations have measured replication rates in samples of psychology studies. Reproducibility Project: Psychology sampled roughly 100 studies from articles published in three top psychology journals in 2008 and distributed the studies across participanting labs. They found an overall replication rate of around 40% [@openscienceconsortium2015]. ManyLabs investigated heterogeneity using short target studies that compared between two conditions each. These study designs were not representative of the psychology literature as a whole, and due to the heterogeneity goal, they had large overall samples across multiple sites. Across Many Labs 1-3, in these high-powered replications, only 29 of 51 target effects (57%) replicated [@klein2014; @klein2018; @ebersole2016]. @camerer2018 included all 21 behavioral social science studies from Nature and Science from 2010-2015 that were feasible; they consulted original authors and had high power to detect effects smaller than those reported. In this well-resourced environment with expert input, the replication rate was around 60%.

@@

Rather than aim for some measure of "true" replicability, it makes more sense to contextualize replication efforts based on their methods and outcome measures. With this lens, we could say that RP:P looked at how well findings in well-known journals can be replicated in a typical psychology lab. Many Labs looked at which well-known two conditions studies replicate with huge samples, and @camerer2018 looked at which prestigious journal findings replicate when conducted in a highly-resourced environment with expert involvement. All of these are potentially desirable estimands depending on what the specific circumstances and questions of interest are.

Most scientific work is conducted by student, so it makes sense for students to conduct replications  [@frank2022]. In our current study, we use student success at replicating an effect as our estimand. In particular, our estimand is the probability that a researcher, on selecting a finding of interest from the literature, can successfully achieve a result satisfactorily close enough to the original that they can build on it in their own work, with all the necessary compromises to the methods and sample of the original that may be required by the constraints of the situation.

Our replication approach reflects this estimand. Our sample of studies is selected based on what studies students were interested in and wanting to replicate, with some filtering for feasibility; this sampling reflects how scientists choose what studies to build on: those that are interesting and relatively doable given methodological and budgetary constraints. All our replications were conducted under short time scales and relatively small budgets, paralleling the constraints many scientists are under when starting new projects. From the point of view of cumulative science, researchers want to know if they can get paradigms to work under their real-world constraints. We use a subjective replication score as our primary metric. Whether one feels confident in the results of a study given a replication is not always dependent on only one outcome measure (ex. interaction term) and particularly not dependent on only one statistical comparison between the two studies (ex. replication is p<.05 same direction as original). This metric avoids bright line distinctions and accommodates the range of outcome measures in our diverse set of studies.

@@

Given the limitations of experimental approaches, correlational approaches are the more popular choice for studying potential predictors of replicability. Correlational approaches depend on data from replications, generally drawing heavily from the same small set of data points. In particular, the RP:P dataset itself is much discussed and reanalyzed [@etz2016;@gilbert2016;@patil2016;@anderson2016] to the point that much of what we think we know about replicability may be overfit to the 100 studies included in in RP:P. More data is needed to identify markers of replicability and targets for potential future interventions.

Our contribution is a new dataset of 176 replications of experimental studies from the social sciences, primarily psychology. These replications were conducted by students in a graduate-level experimental methods class between 2011 and 2022 as individual course projects. We investigated statistical and experimental-design predictors of replicability in this dataset and found that within-subjects designs and studies with large standardized effect sizes were positively correlated with replication success.

@@

Researchers use the psychological literature as a source of empirical results that they can build upon and extend as part of cumulative science. When these findings don't replicate, the attempts to extend them are a waste of time and resources.  In order to eventually reduce this waste, we need to be able to identify when results can support cumulative scientific progress and what study features are predictive of this. However, limited numbers of replications and limited research into specific predictors of replication failure mean that the reasons for non-replications are not well understood.

Here, we take a functional approach to assessing replicability, framing both our methods and interpretation around the idea of whether work can be repeated by an early-career scientist. We took advantage of 11 years of graduate student replication projects to look at correlational predictors of replication in a previously-unused dataset. In line with previous results, we found a `r round(pluck(sub_rep_rate,1))`% replication rate, with some studies showing effect sizes similar to the original and others much smaller. When we looked at individual correlates of replicability, within-subjects designs, work in the subfield of cognitive psychology, and the original and replication both using online samples stood out as the strongest correlates. As many of these predictors interrelate with one another, we ran regularized regressions with all the predictors at once. Due to our small sample, model estimates were uncertain, but within-subjects designs and large original effect sizes were the strongest predictors.

<!-- contributions and takehome  -->

Replication results should be interpreted in light of their methods and estimand. Given our sample, we are able to estimate the correlates of studies replicating when the replications are conducted online, by graduate students with limited time and budget. We do not interpret our non-replications as indicating the original results were false positives (presumably some were and some weren't). There are many possible reasons for the non-replications in this sample. In some cases, the problem may be with the replication, such as too few participants, many exclusions for failed attention checks, or participants speeding through the study. When these issues are diagnosed, they suggest possible ways to "rescue" the replication by increasing the sample or changing the interface, without altering the underlying experiment; thus, while the replication did not succeed, after some troubleshooting, students may still be able to extend the work in the future. In other cases, there were a priori reasons to distrust the original study, such as exclusion criteria that seemed post-hoc or high-order interaction terms with a small sample. That said, not all scientists recognize the same factors as potential indications of low power or questionable research practices; students conducting these replications generally expected them to succeed. In many non-replication cases, it was unclear why the results failed to replicate.

The same issue that may cause a study not to replicate under constrained circumstances (despite hypothetically replicating under more favorable circumstances such as expert administration or larger budgets) will also plague attempts to build off those studies in constrained circumstances. Thus, we believe it is relevant to consider how well studies replicate under the limitations of real world resource and expertise constraints.

@@

### 2023-05-04 paper/manuscript.tex
another pass at intro and disc

Cumulative science requires foundational empirical results that are robust enough to support theory construction and future experimental extension. Scientists often treat publication in a scientific journal as a signal that a result was (likely to be) true, which leads scientists to build on findings without verifying them first. The replication crisis called into question the tacit assumption that most of the literature was robust and would replicate. Certain prominent findings failed to replicate in multi-site replication attempts (ex. terror management theory, \protect\hyperlink{ref-klein2022}{Klein et al. 2022}, ego-depletion, \protect\hyperlink{ref-hagger2016}{Hagger et al. 2016}), and a large-scale replication project pegged the replication rate for findings in top-tier psychology journals at around 40\% (\protect\hyperlink{ref-openscienceconsortium2015}{Open Science Consortium 2015}). When the trust in the literature mismatches the robustness results, many scientists can waste time and resources becoming frustrated pursuing extensions to a popular, but unreliable result. This seems to be the current situation of the literature, which leads to question: what do we do to minimize the waste?

From a policy perspective, we need to understand the landscape of the problem before we can have research-informed science policy interventions. Thus, we might want to know 1) what quantity to measure if we want to capture frustration and waste due to non-cumulative findings and 2) from a descriptive perspective, what types of studies are most at risk for this issue. Such measurements have been the focus of much prior work, but there is limited consensus on what is being estimated.

Three large-scale investigations have addressed replication rates in psychology. Reproducibility Project: Psychology, mentioned above, sampled roughly 100 studies from articles published in three top psychology journals in 2008 and they found an overall replication rate of around 40\% (\protect\hyperlink{ref-openscienceconsortium2015}{Open Science Consortium 2015}). ManyLabs investigated heterogeneity using short target studies that compared between two conditions each. These study designs were not representative of the psychology literature as a whole, and due to the heterogeneity goal, they had large overall samples across multiple sites. Across Many Labs 1-3, in these high-powered replications, only 29 of 51 target effects (57\%) replicated (\protect\hyperlink{ref-klein2014}{Klein et al. 2014}, \protect\hyperlink{ref-ebersole2016}{Ebersole et al. 2016}, \protect\hyperlink{ref-klein2018}{Klein et al. 2018}). Camerer et al. (\protect\hyperlink{ref-camerer2018}{2018}) replicated all 21 behavioral social science studies from Nature and Science from 2010-2015 that were feasible; they consulted original authors and had high power to detect effects smaller than those reported. In this well-resourced environment with expert input, the replication rate was around 60\%. These studies all measured replication rates, but the details of their methods and outcome measures varied.

@@

Rather than aim for some measure of ``true'' replicability, it makes more sense to contextualize replication efforts based on their methods and outcome measures. With this lens, we could say that RP:P is looking at how well findings in well-known journals can be replicated in typical circumstances. Many Labs looked at which well-known two conditions studies replicate with huge samples, and Camerer et al. (\protect\hyperlink{ref-camerer2018}{2018}) was looking at what replicates when conducted in a highly-resourced environment with expert involvement. All of these are pontentially desirable estimands depending on what the specific circumstances and questions of interest are.

From the point of view of enabling cumulative science, an estimand of interest is how well work can be replicated by students, as students conduct most scientific work (\protect\hyperlink{ref-frank2022}{\textbf{frank2022?}}). In our current study, we use student success at replicating an effect as our estimand. In particular, our estimand is the probability that a researcher, on selecting a finding of interest from the literature, can successfully achieve a result satisfactorily close enough to the original that they can build on it in their own work, with all the necessary compromises to the methods and sample of the original that may be required by the constraints of the situation.

Our replication approach reflects this estimand. Our sample of studies is selected based on what studies students were interested in and wanting to replicate, with some filtering for feasibility; this sampling reflects how scientists choose what studies to build on: those that are interesting and relatively doable given methodological and budgetary constraints.

We use a subjective replication score as our primary metric. Whether one feels confident in the results of a study given a replication is not always dependent on only one outcome measure (ex. interaction term) and particularly not dependent on only one statistical comparison between the two studies (ex. replication is p\textless.05 same direction as original). This metric avoids bright line distinctions and accommodates the range of outcome measures in our diverse set of studies.

All our replications were conducted under short time scales and relatively small budgets, paralleling the constraints many scientists are under when starting new projects. From the point of view of cumulative science, researchers want to know if they can get paradigms to work under their real-world constraints.

@@

Given the limitations of experimental approaches, we have to rely on correlational approaches for now. Correlational approaches depend on data from replications, generally drawing heavily from the same small set of data points. In particular, the RP:P dataset itself is much discussed and reanalyzed (\protect\hyperlink{ref-anderson2016}{Anderson et al. 2016}, \protect\hyperlink{ref-etz2016}{Etz \& Vandekerckhove 2016}, \protect\hyperlink{ref-gilbert2016}{Gilbert et al. 2016}, \protect\hyperlink{ref-patil2016}{Patil et al. 2016}) to the point that much of what we think we know about replicability may be overfit to the 100 studies included in in RP:P. We need more data to find potential targets of concern and intervention.

Our contribution is a new dataset of 176 replications of experimental studies from the social sciences, primarily psychology. These replications were conducted by students in graduate-level experimental methods class between 2011 and 2022 as individual course projects. We investigated statistical and experimental-design predictors of replicability in this dataset and found that within-subjects designs and studies with large standardized effect sizes were positively correlated with replication success.

@@

\hypertarget{question-summary-and-takehomes}{%
\subsection{question, summary, and takehomes}\label{question-summary-and-takehomes}}

NEED TO REDO!
MAY NEED SMOOTHER TRANSITIONS THROUGHOUT
Prior large scale replications of psychology findings have estimated the replication rate at somewhere around one half, which intuitively feels low. However, limited numbers of replications and limited research into specific predictors of replication failure mean that the reasons for non-replications are not well understood.

Overall, we take a functional approach to assessing replicability, by framing both our methods and interpretation around the idea of whether work can be repeated or built on by an early-career scientist.

Here we took advantage of 11 years of graduate student replication projects to look at correlational predictors of replication in a previously-unused dataset. In line with previous results, we found a 49\% replication rate, with some studies showing effect sizes similar to the original and others much smaller. When we looked at individual correlates of replicability, within-subjects designs, work in the subfield of cognitive psychology, and the original and replication both using online samples stood out as the strongest correlates. As many of these predictors interrelate with one another, we ran regularized regressions with all the predictors at once. Due to our small sample, model estimates were uncertain, but within-subjects designs and large original effect sizes were the strongest predictors.

The same issue that may cause a study not to replicate under constrained circumstances (despite hypothetically replicating under more favorable circumstances such as expert administration or larger budgets) will also plague attempts to build off those studies in constrained circumstances. Thus, we believe it is relevant to estimate replicability under the limitations of real world resource and expertise constraints.
\#\# intepretation - replication in light of the goal

Replication results should be interpreted in light of their methods and estimand.

Given our sample, we are able to estimate the correlates of studies replicating when the replications are conducted online, by graduate students with limited time and budget. We do not interpret our non-replications as indicating the original results were false positives (presumably some were and some weren't). There are many possible reasons for the non-replications in this sample. In some cases, the problem may be with the replication, such as too few participants, many exclusions for failed attention checks, or participants speeding through the study. When these issues are diagnosed, they suggest possible ways to ``rescue'' the replication by increasing the sample or changing the interface, without altering the underlying experiment; thus, while the replication did not succeed, after some troubleshooting, students may still be able to extend the work in the future. In other cases, there were a priori reasons to distrust the original study, such as exclusion criteria that seemed post-hoc or high-order interaction terms with a small sample. That said, not all scientists recognize the same factors as potential indications of low power or questionable research practices; students conducting these replications generally expected them to succeed. In many non-replication cases, it was unclear why the results failed to replicate.

\hypertarget{limitations}{%
\subsection{limitations}\label{limitations}}

@@

\hypertarget{conclusion}{%
\subsection{conclusion}\label{conclusion}}

>>>>

Cumulative scientific progress requires empirical results that are robust enough to support theory construction and future extensions. Yet in psychology, some prominent individual findings have failed to replicate in multi-site replication attempts (ex. terror management theory, \protect\hyperlink{ref-klein2022}{Klein et al. 2022}, ego-depletion, \protect\hyperlink{ref-hagger2016}{Hagger et al. 2016}), and a large-scale replication project pegged the replication rate for findings in top-tier psychology journals at around 40\% (\protect\hyperlink{ref-openscienceconsortium2015}{Open Science Consortium 2015}). When scientists treat publication as a signal of truth and attempt to build on results without verifying them first, they can become frustrated pursuing extensions to a popular, but unreliable result. As each failed extension does not directly contradict the original result, many scientists may waste a lot of time and resources pursuing results where there may be none. This leads to a question: what do we do to minimize the waste?

{[}This feels like we're setting up for the advice: don't try to extend anything without replicating it first, not sure how to shift to the policy issue.{]}

From a policy perspective, we need to understand the landscape of the problem before we can have research-informed science policy interventions. Thus, we might want to know 1) what quantity to measure if we want to capture frustration and waste due to non-cumulative findings and 2) from a descriptive perspective, what types of studies are most at risk for this issue. Such measurements have been the focus of much prior work around replicability, but there is limited consensus on what is being estimated.

Three large-scale investigations have measured replication rates in samples of psychology studies. Reproducibility Project: Psychology sampled roughly 100 studies from articles published in three top psychology journals in 2008 and distributed the studies across participanting labs. They found an overall replication rate of around 40\% (\protect\hyperlink{ref-openscienceconsortium2015}{Open Science Consortium 2015}). ManyLabs investigated heterogeneity using short target studies that compared between two conditions each. These study designs were not representative of the psychology literature as a whole, and due to the heterogeneity goal, they had large overall samples across multiple sites. Across Many Labs 1-3, in these high-powered replications, only 29 of 51 target effects (57\%) replicated (\protect\hyperlink{ref-klein2014}{Klein et al. 2014}, \protect\hyperlink{ref-ebersole2016}{Ebersole et al. 2016}, \protect\hyperlink{ref-klein2018}{Klein et al. 2018}). Camerer et al. (\protect\hyperlink{ref-camerer2018}{2018}) included all 21 behavioral social science studies from Nature and Science from 2010-2015 that were feasible; they consulted original authors and had high power to detect effects smaller than those reported. In this well-resourced environment with expert input, the replication rate was around 60\%.

@@

Rather than aim for some measure of ``true'' replicability, it makes more sense to contextualize replication efforts based on their methods and outcome measures. With this lens, we could say that RP:P looked at how well findings in well-known journals can be replicated in a typical psychology lab. Many Labs looked at which well-known two conditions studies replicate with huge samples, and Camerer et al. (\protect\hyperlink{ref-camerer2018}{2018}) looked at which prestigious journal findings replicate when conducted in a highly-resourced environment with expert involvement. All of these are potentially desirable estimands depending on what the specific circumstances and questions of interest are.

Most scientific work is conducted by student, so it makes sense for students to conduct replications (\protect\hyperlink{ref-frank2022}{\textbf{frank2022?}}). In our current study, we use student success at replicating an effect as our estimand. In particular, our estimand is the probability that a researcher, on selecting a finding of interest from the literature, can successfully achieve a result satisfactorily close enough to the original that they can build on it in their own work, with all the necessary compromises to the methods and sample of the original that may be required by the constraints of the situation.

Our replication approach reflects this estimand. Our sample of studies is selected based on what studies students were interested in and wanting to replicate, with some filtering for feasibility; this sampling reflects how scientists choose what studies to build on: those that are interesting and relatively doable given methodological and budgetary constraints. All our replications were conducted under short time scales and relatively small budgets, paralleling the constraints many scientists are under when starting new projects. From the point of view of cumulative science, researchers want to know if they can get paradigms to work under their real-world constraints. We use a subjective replication score as our primary metric. Whether one feels confident in the results of a study given a replication is not always dependent on only one outcome measure (ex. interaction term) and particularly not dependent on only one statistical comparison between the two studies (ex. replication is p\textless.05 same direction as original). This metric avoids bright line distinctions and accommodates the range of outcome measures in our diverse set of studies.

@@

Given the limitations of experimental approaches, correlational approaches are the more popular choice for studying potential predictors of replicability. Correlational approaches depend on data from replications, generally drawing heavily from the same small set of data points. In particular, the RP:P dataset itself is much discussed and reanalyzed (\protect\hyperlink{ref-anderson2016}{Anderson et al. 2016}, \protect\hyperlink{ref-etz2016}{Etz \& Vandekerckhove 2016}, \protect\hyperlink{ref-gilbert2016}{Gilbert et al. 2016}, \protect\hyperlink{ref-patil2016}{Patil et al. 2016}) to the point that much of what we think we know about replicability may be overfit to the 100 studies included in in RP:P. More data is needed to identify markers of replicability and targets for potential future interventions.

Our contribution is a new dataset of 176 replications of experimental studies from the social sciences, primarily psychology. These replications were conducted by students in a graduate-level experimental methods class between 2011 and 2022 as individual course projects. We investigated statistical and experimental-design predictors of replicability in this dataset and found that within-subjects designs and studies with large standardized effect sizes were positively correlated with replication success.

@@

Researchers use the psychological literature as a source of empirical results that they can build upon and extend as part of cumulative science. When these findings don't replicate, the attempts to extend them are a waste of time and resources. In order to eventually reduce this waste, we need to be able to identify when results can support cumulative scientific progress and what study features are predictive of this. However, limited numbers of replications and limited research into specific predictors of replication failure mean that the reasons for non-replications are not well understood.

Here, we take a functional approach to assessing replicability, framing both our methods and interpretation around the idea of whether work can be repeated by an early-career scientist. We took advantage of 11 years of graduate student replication projects to look at correlational predictors of replication in a previously-unused dataset. In line with previous results, we found a 49\% replication rate, with some studies showing effect sizes similar to the original and others much smaller. When we looked at individual correlates of replicability, within-subjects designs, work in the subfield of cognitive psychology, and the original and replication both using online samples stood out as the strongest correlates. As many of these predictors interrelate with one another, we ran regularized regressions with all the predictors at once. Due to our small sample, model estimates were uncertain, but within-subjects designs and large original effect sizes were the strongest predictors.

Replication results should be interpreted in light of their methods and estimand. Given our sample, we are able to estimate the correlates of studies replicating when the replications are conducted online, by graduate students with limited time and budget. We do not interpret our non-replications as indicating the original results were false positives (presumably some were and some weren't). There are many possible reasons for the non-replications in this sample. In some cases, the problem may be with the replication, such as too few participants, many exclusions for failed attention checks, or participants speeding through the study. When these issues are diagnosed, they suggest possible ways to ``rescue'' the replication by increasing the sample or changing the interface, without altering the underlying experiment; thus, while the replication did not succeed, after some troubleshooting, students may still be able to extend the work in the future. In other cases, there were a priori reasons to distrust the original study, such as exclusion criteria that seemed post-hoc or high-order interaction terms with a small sample. That said, not all scientists recognize the same factors as potential indications of low power or questionable research practices; students conducting these replications generally expected them to succeed. In many non-replication cases, it was unclear why the results failed to replicate.

The same issue that may cause a study not to replicate under constrained circumstances (despite hypothetically replicating under more favorable circumstances such as expert administration or larger budgets) will also plague attempts to build off those studies in constrained circumstances. Thus, we believe it is relevant to consider how well studies replicate under the limitations of real world resource and expertise constraints.

@@
